A Case Study in Preserving a High Energy Physics Application

### 2014-12-18 paper.tex
Change the template to ICCS
	remove old template and related files

\documentclass{sig-alternate}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\hyphenation{resour-ces}
\hyphenation{approac-hes}
\hyphenation{har-der}
\hyphenation{spe-cifically}
\makeatletter
\def\@copyrightspace{\relax}
\makeatother
\begin{document}

\title{A Case Study in Preserving a\\High Energy Physics Application}
\subtitle{DASPOS Technical Report \#2}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

@@

\begin{figure}[t]
\centering
\includegraphics[width=.8\columnwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{figure}

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of actually used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
\caption{Version Evolution}
\label{fig:version-evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{solution3.eps}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
\label{fig:workflow-parrot}
\end{figure*}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \bf Path used in Program & \bf Actual Location \\ \hline
    {\tt /} & {\tt /tmp/package-hep} \\ \hline
    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
    {\tt /dev} & {\tt /dev} \\ \hline
    {\tt ...} & {\tt ...}\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files    & 1632         & 15642\\ 
\hline
    Empty Files    & 14273        & 263\\
\hline
    Directories    & 1549         & 1549\\ 
\hline
    Symbolic Links & 4614         & 4614 \\
\hline
    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{git-syscall.eps}
\caption{Exec Syscalls of a git command}
\label{fig:git-syscall}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{http_packet.eps}
\caption{HTTP Request and Response}
\label{fig:http_packet}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{url_redirection.eps}
\caption{An Example of URL Redirection}
\label{fig:url_redirection}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Original Script and Reduced Package}
    \label{table:time-2nd3rd}
\end{table}

@@

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
    Original &  Red Hat  & 64 & 125 & 13min 04s\\  
    Machine& 5.10 &&&\\ \hline
    KVM & CentOS & 4 & 2 & 21min 38s\\
    (Notre Dame)&5.10 &&&\\ \hline
    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
    (EC2) &5.9 &&&\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{preservation-integration.eps}
\caption{Preserving Multiple Artifacts}
\label{fig:Preservation integration}
\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{cclpapers,this}

>>>>

\documentclass[procedia]{easychair}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\hyphenation{resour-ces}
\hyphenation{approac-hes}
\hyphenation{har-der}
\hyphenation{spe-cifically}
\makeatletter
\def\@copyrightspace{\relax}
\makeatother

\title{A Case Study in Preserving a High Energy Physics Application}

% \titlerunning{} has to be set to either the main title or its shorter
% version for the running heads. When processed by
% EasyChair, this command is mandatory: a document without \titlerunning
% will be rejected by EasyChair

\titlerunning{A Case Study in Preserving a High Energy Physics Application}

\author{
	Haiyan Meng\inst{1}
\and
	Matthias Wolf\inst{2}
\and
	Douglas Thain\inst{3}
}
\institute{
	Department of Computer Science and Engineering,
	University of Notre Dame,
	Notre Dame, Indiana, USA
	\email{hmeng@nd.edu}
\and
	Department of Physics,
	University of Notre Dame,
	Notre Dame, Indiana, USA
	\email{mwolf3@nd.edu}
\and
	Department of Computer Science and Engineering,
	University of Notre Dame,
	Notre Dame, Indiana, USA
	\email{dthain@nd.edu}
}

%  \authorrunning{} has to be set for the shorter version of the authors' names;
% otherwise a warning will be rendered in the running heads. When processed by
% EasyChair, this command is mandatory: a document without \authorrunning
% will be rejected by EasyChair

\authorrunning{Meng, Wolf and Thain}

\begin{document}

\maketitle

\keywords{}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.8\textwidth]{version-evolution.eps}
\caption{Version Evolution}
\label{fig:version-evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{solution3.eps}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
\label{fig:workflow-parrot}
\end{figure*}

@@

\begin{table}
    \centering
    \begin{tabular}{ll}
    \hline
    \bf Path used in Program & \bf Actual Location \\ \hline
    {\tt /} & {\tt /tmp/package-hep} \\ \hline
    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
    {\tt /dev} & {\tt /dev} \\ \hline
    {\tt ...} & {\tt ...}\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{rrr}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files    & 1632         & 15642\\ 
\hline
    Empty Files    & 14273        & 263\\
\hline
    Directories    & 1549         & 1549\\ 
\hline
    Symbolic Links & 4614         & 4614 \\
\hline
    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{git-syscall.eps}
\caption{Exec Syscalls of a git command}
\label{fig:git-syscall}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{http_packet.eps}
\caption{HTTP Request and Response}
\label{fig:http_packet}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{url_redirection.eps}
\caption{An Example of URL Redirection}
\label{fig:url_redirection}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{lrr}
    \hline
    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Original Script and Reduced Package}
    \label{table:time-2nd3rd}
\end{table}

@@

\begin{table}
	\centering
	    \begin{tabular}{llrrr}
	        \hline
	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
	        \hline
	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
	    \end{tabular}
	    \caption{Data and Code Used by Tau Roast}
	    \label{table:size-original-real}
\end{table}
%	\begin{tablenotes}
%	      \small
%	      \item The first column illustrates the total size of each data and software source; 
%	            the second column illustrates the size of the named files from each source;
%	            the third column illustrates the size of actually used data from each source.
%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
%	    \end{tablenotes}

@@

\begin{table}
    \centering
    \begin{tabular}{lrrrr}
    \hline
    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{preservation-integration.eps}
\caption{Preserving Multiple Artifacts}
\label{fig:Preservation integration}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{cclpapers,this}
